---
title: "Analysis of sufficient terms and conditions"
author: "Ingo Rohlfing, Ayjeren Bekmuratovna R."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis-of-sufficient-terms-and-conditions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  error = T,
  collapse = TRUE,
  comment = "#>"
)
```

We load the packages needed for illustrating a robustness assessment on the level of individual sufficient terms and single conditions.
```{r load package, warning = F, message = F}
library(QCArobust)
library(dplyr) # data wrangling
library(knitr) # nicer html tables
```

The original robustness analysis by 
[Skaaning (2011)](http://10.599/004912451404818) is the basis for our empirical
illustration. We import a list of solutions presented in table 3 of the article.
It summarizes results for the choice of different calibration anchors for 
crisp-set QCA.

```{r Skaaning csqca anchors}
# load Skaaning (2011) data from table 3
data("Skaaning_table3")
```

## Analysis of sufficient terms
A *term* is any element of a solution that is in itself sufficient for the 
outcome. This can be a single condition or a single configuration (or 
conjunction), depending on the solution. The solution 
$A + BC \Leftrightarrow Y$ has $A$ and $BC$ as sufficient terms. On the second, 
medium level of aggregation, the solutions are decomposed into their individual 
sufficient terms. The `configurations_robust()` function decomposes solutions 
into its individual terms (also if the term is a single condition; usually it 
is a configuration) and produces an *Upset plot*. The horizontal bars of an 
Upset plot summarize the frequency of a term across all solutions. The vertical 
bars summarize the *cooccurrence* of terms in solutions. The argument `nsets` 
specifies the number of bars that should be plotted (also for 
`conditions_robust()`). The default is 5. 

```{r, eval = T, fig.width = 7, fig.height = 7}
skaaning_terms <- configurations_robust(Skaaning_table3)
skaaning_terms
```


### Subsetting terms by consistency values
to be done

## Analysis of individual conditions
The function `conditions_robust()` does the same as `configurations_robust()` 
for single conditions. For example, the condition *ind* occurs in 33 solutions. 
In 27 solutions, *ind* cooccurs with *DEV* and *STA* and 6 times with *LIT*, 
*DEV* and *STA*.

```{r, fig.width=7, fig.height=7, fig.align='center'}
conditions_robust(Skaaning_table3, nsets = 10) -> conds_plot
conds_plot
```

The `UpsetR` package that is used for plotting stores a cooccurrence dataset 
under `.$New_data`. 

```{r}
kable(head(conds_plot$New_data))
```

With a little bit of data wrangling, one can calculate the numbers plotted in 
an UpSet plot. Calculating the cooccurrence data (vertical bars).

```{r}
conds_plot$New_data %>% 
  group_by(DEV, STA, ind, C, LIT) %>% 
  summarize(cooccurrence = n()) %>% 
  kable(.)
```

Calculating the total occurence by condition.

```{r}
kable(colSums(conds_plot$New_data))
```


