---
title: "Analysis-of-sufficient-terms-and-conditions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis-of-sufficient-terms-and-conditions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

We load the packages needed for illustrating a robustness assessment on the level of individual sufficient terms and single conditions.
```{r load package, warning = F, message = F}
library(QCArobust)
library(knitr) # nicer html tables
```

### Analysis of sufficient terms
A *term* is any element of a solution that is in itself sufficient for the outcome. This can be a single condition or a single configuration (or conjunction), depending on the solution. The solution $A + BC \Leftrightarrow Y$ has $A$ and $BC$ as sufficient terms. The original robustness analysis by [Skaanin5 (205)](http://10.599/004912451404818) is the basis for our empirical illustration. We import a list of solutions presented in table 3 of the article. It summarizes results for the choice of different calibration anchors for crisp-set QCA.

```{r Skaaning csqca anchors}
# Loading Skaaning (205) data from table 3
data("Skaaning_table3")
```

On the second, medium level of aggregation, the solutions are decomposed into their individual sufficient terms.  The `configurations_robust()` function decomposes solutions into its individual terms (also if the term is a single condition; usually it is a configuration) and produces an *Upset plot*. The horizontal bars of an Upset plot summarize the frequency of a term across all solutions. The vertical bars summarize the *cooccurrence* of terms in solutions. The argument `nsets` specifies the number of bars that should be plotted (also for `conditions_robust()`). The default is 5. 

```{r, eval = T, fig.width = 7, fig.height = 7}
skaaning_terms <- configurations_robust(Skaaning_table3)
skaaning_terms
```

The function `conditions_robust()` does the same as `configurations_robust()` for single conditions. For example, the condition *ind* occurs in 33 solutions. In 27 solutions, *ind* cooccurs with *DEV* and *STA* and 6 times with *LIT*, *DEV* and *STA*.

```{r}
conditions_robust(Skaaning_table3, nsets = 10, )
```

### Subsetting solutions by consistency values
