---
title: "Preparing QCA solutions for analysis"
author: "Ingo Rohlfing, Ayjeren Bekmuratovna R."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Preparing QCA solutions for analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  error = T,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(QCArobust)
library(QCA) # for truth tables and QCA solutions 
```

The QCA solutions have to be stored as a *list* in order to use them as input
for the three main functions `solutions_robust()`, `configurations_robust()` 
and `conditions_robust()`. 

```{r data-prep}
set.seed(834) # seed for random number generation
# create hypothetical crisp-set data
crisp_data1 <- data.frame(A = rbinom(50, 1, 0.5),
                          B = rbinom(50, 1, 0.5),
                          C = rbinom(50, 1, 0.5),
                          D = rbinom(50, 1, 0.5),
                          Y = rbinom(50, 1, 0.5))
# create truth table
tt1 <- truthTable(data = crisp_data1, 
                  outcome = "Y",
                  sort = "incl, n")
# derive conservative solution (type does not matter here)
sol1 <- minimize(tt1,
                 include = "1")

# repeat process for hypothetical second dataset
crisp_data2 <- data.frame(A = rbinom(50, 1, 0.5),
                          B = rbinom(50, 1, 0.5),
                          C = rbinom(50, 1, 0.5),
                          D = rbinom(50, 1, 0.5),
                          Y = rbinom(50, 1, 0.5))
# create truth table
tt2 <- truthTable(data = crisp_data2, 
                  outcome = "Y",
                  sort = "incl, n")
# derive conservative solution (type does not matter here)
sol2 <- minimize(tt2,
                 include = "1")
```

The solution objects produced with the [QCA package](https://cran.r-project.org/package=QCA) 
need to combined in a list to process them further with the *QCArobust* package. 
One only needs to include the solution attribute (`$solution`$) from the complete
solution in a list of solutions.

```{r create-list}
sols_list <- list(sol1$solution, sol2$solution) 
sols_list
```

When all solutions have been included in the list, one can use it with each of
the three functions for aggregating the results.

```{r}
QCArobust::solutions_robust(sols_list) 
QCArobust::conditions_robust(sols_list) 
QCArobust::configurations_robust(sols_list) 

```

