---
title: "Working with the QCAviz package"
author: "Ingo Rohlfing, Ayjeren Rozyjumayeva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(QCAviz)
```


QCA solutions that a researcher wants to aggregate can be created in different ways.

## Manual import of solutions
We use the original robustness analysis by Skaaning to illzstrate the manual import of solutions. (Skaaning, Svend-Erik (2011): Assessing the Robustness of Crisp-Set and Fuzzy-Set QCA Results. *Sociological Methods & Research* 40 (2): 391-408. [published version](http://10.1177/0049124111404818))

The following solutions are extracted from table 3 in the article that summarizes results for the choice of different calibration anchors for crisp-set QCA.
```{r Skaaning csqca anchors}
# crisp-set solutions with different anchors
one <- replicate(28, "DEV*STA")
two <- replicate(27, "DEV*ind+DEV*STA")
three <- replicate(165, "C")
four <- replicate(18, "DEV*LIT*STA")
five <- replicate(6, "DEV*STA+DEV*LIT*ind")
# combining solutions in list
Skaaning_csanchors <- list(one, two, three, four, five)
```

On the highest level of aggregation, one simply looks at the frequencies of the solutions.
```{r Skaaning csqca anchors sols}
sols_upset(Skaaning_csanchors, nsets = 5)
```

On the second, medium level of aggregation, the solutions are decomposed into their configurations. The `config_upset()` function serves this purpose.
```{r Skaaning csqca anchors configs}
config_upset(Skaaning_csanchors, nsets = 10)
```

