---
title: "Working with the QCAviz package"
author: "Ingo Rohlfing, Ayjeren Rozyjumayeva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

QCA solutions that a researcher wants to aggregate can be created in different ways.

## Manual import of solutions
We use the original robustness analysis by Skaaning to illzstrate the manual import of solutions. (Skaaning, Svend-Erik (2011): Assessing the Robustness of Crisp-Set and Fuzzy-Set QCA Results. *Sociological Methods & Research* 40 (2): 391-408. [published version](http://10.1177/0049124111404818))

The following solutions are extracted from table 3 in the article that summarizes results for the choice of different calibration anchors for crisp-set QCA.
```{r Skaaning csqca anchors}
# crisp-set solutions with different anchors
one <- replicate(28, "DEV*STA")
two <- replicate(27, "DEV*ind+DEV*STA")
three <- replicate(165, "C")
four <- replicate(18, "DEV*LIT*STA")
five <- replicate(6, "DEV*STA+DEV*LIT*ind")
# combining solutions in list
Skaaning_csanchors <- list(one, two, three, four, five)
```

On the highest level of aggregation, one simply looks at the frequencies of the solutions.
The function does not exist anymore.
```{r Skaaning csqca anchors sols}
skaaning_sols <- sols_barplot(Skaaning_csanchors)
skaaning_sols + 
  scale_x_discrete("") +
  scale_y_continuous("frequency") +
  theme_classic() +
  theme(legend.position = 'none',
        plot.title = element_blank())
ggsave("Skaaning_solutions.png", width = 6, height = 4)
```

On the second, medium level of aggregation, the solutions are decomposed into their configurations. The `config_upset()` function serves this purpose. This should be used now with the config_upset_h() version of the function.
```{r Skaaning csqca anchors configs}
skaaning_configs <- config_upset_h(Skaaning_csanchors, nsets = 100)
png("Skaaning_configs.png", width = 600, height = 400, res = "100")
print(skaaning_configs)
dev.off()
```

```{r Skaaning csqca anchors conditions}
skaaning_conds <- conds_upset(Skaaning_csanchors, nsets = 200)
png("Skaaning_conds.png", width = 600, height = 400, res = "100")
print(skaaning_conds)
dev.off()
```

Adding (to be edited later) application of the functions that allow for selection of the consistenc values.

```{r}
data("hinter")
hinter <- hinter %>% 
  mutate(POScal = round(calibrate(pos, thresholds = "-2.4, -0.15, 1.4"), digits = 2)) %>% 
  mutate(AMBcal = round(calibrate(ambition, thresholds = "0.01, 0.1205, 0.2"), digits = 2)) %>% 
  mutate(CRcal = round(calibrate(CR, thresholds = c("5, 52, 95")), digits = 2)) %>% 
  mutate(DCcal = round(calibrate(DC, thresholds = c("33.5, 47, 55")), digits = 2)) %>% 
  mutate(EFFcal = round(calibrate(EFF, thresholds = c("0.7, 1.175, 2.065")), digits = 2)) %>%
  mutate(COMcal = round(calibrate(COM, thresholds = c("4.28, 4.86, 5.285")), digits = 2))

ttpos <- truthTable(data = hinter, outcome = "POScal", neg.out = FALSE,
                    conditions = c("AMBcal", "CRcal", "DCcal", 
                                   "EFFcal", "COMcal", "PRG"),
                    n.cut = 1, incl.cut1 = 0.837, sort.by = c("incl", "n"), 
                    complete = F, decreasing = T, show.cases = TRUE, PRI = F)

poscons <- minimize(ttpos, details = T, 
                 explain = "1", include = "1",
                 all.sol = T)

```


Applying the selector function itself and then the function within the UpSetR wrap function.

```{r}
dt.selector(poscons)
dt.selector(poscons, con.thresh = 0.85)

#being re-written
#list.selector(solutionslist)
#list.selector(solutionslist, con.thresh = 0.85)
```


Usage of the selectors within the QCAViz functions
```{r}
solutionslist <- list(poscons, poscons)

#the configurations that are subset
config_upset(poscons, const = TRUE, y = 0.85, nsets = 10)

#all of the configurations
config_upset(poscons, nsets = 10)
```


Applying the functions to Krogslund et al. (PA, 2015)
Initially on the naive model 1 (referred to as ka_model_1_sim)

```{r}
model_1 <- read.csv("ka_model_1_sim.csv")

#conditions
kcp <- conds_upset(model_1$Configurations, nsets = 200)
kcp <- config_upset_t(model_1$Configurations, nsets = 378)

conds_upset(model_1$Configurations, nsets = 162)
config_upset_t(model_1$Configurations, nsets = 387)
```


The rest of the models (titled for the sake of clarity as model_n)
model_1 (is the model presented in the chunk above).

```{r}
model_2 <- read.csv("ka_model_1_ncut1_error.csv")
model_3 <- read.csv("model_2_ncut1_error.csv")
model_4 <- read.csv("model_2_sim.csv")
model_5 <- read.csv("model_ncut2_error.csv")
model_6 <- read.csv("model_sim.csv")
```

Conditions function
```{r}
conds_upset(model_2$Configurations, nsets = 200)
conds_upset(model_3$Configurations, nsets = 500)
conds_upset(model_4$Configurations, nsets = 300)
conds_upset(model_5$Configurations, nsets = 400)
conds_upset(model_6$Configurations, nsets = 500)
```


Configurations applied
```{r}
config_upset_t(model_2$Configurations, nsets = 300)
config_upset_t(model_3$Configurations, nsets = 300)
config_upset_t(model_4$Configurations, nsets = 400)
config_upset_t(model_5$Configurations, nsets = 500)
config_upset_t(model_6$Configurations, nsets = 400)

```


Applying the functions to the Böller Study


Important: 
1. the process first needs the derivation of solutions.
2. The cases with a single condition do not work within the UpSetR environment.

The conditions
```{r}
conds_upset(negcons$solution, nsets = 15)
conds_upset(negpars$solution, nsets = 13)
conds_upset(poscons$solution, nsets = 5)
conds_upset(neginter$solution, nsets = 15)

#the non-functioning cases
conds_upset(posinter$solution, nsets = 5) #does not work bc there is a single condition!
conds_upset(pospars$solution, nsets = 5)  #does not work bc there is a single condition!
```


The configurations
The same notes as above apply
```{r}

config_upset(neginter, nsets = 4)
config_upset(poscons, nsets = 13)
config_upset(negcons, nsets = 13)
config_upset(negpars, nsets = 12)

#the non-functioning cases
config_upset(pospars, nsets = 10) #does not work bc there is a sngl condition
config_upset(posinter, nsets = 14) #does not work bc there is a sngl condition
```


Pulling solutions (will be taken out of the 
final version of the vignette, I just want to check if 
the functions for hand pulled solutions work)

Pulling all of the solutions
```{r}
allsols <- c(posinter$solution, poscons$solution, pospars$solution, 
                 neginter$solution, negcons$solution, negpars$solution)
```

Checking the main pooled solution functions
```{r}
conds_upset_h(allsols, nsets = 10)
config_upset_h(allsols, nsets = 10)
```


Adding the simulated dataset fr Hinter-Leitner study
```{r}
library(QCAsummary)

#Simulating and reducing data
data("hinter")
data("arg1")
data("arg2")

#15 fuzzy sets
m_fuzzy <- dat_fuzzy(arg1, arg2, n = 5,
                     case = hinter$case, outcome = hinter$PRG)

#truth tables
temp_dta <- truth_function(df = m_fuzzy, outcome = "pos",
                           conditions = c("ambition", "CR", "DC", "EFF", "COM", "outcome"),
                           n.cut = 1, incl.cut1 = 0.637)

```


Deriving the parsimonious solutions and plotting it
with the QCAviz conditions function

```{r warning=FALSE}
sol.p <- reduced_p(temp_dta)
sol.pars <- solutions(sol.p)

#plotting the conditions
QCAviz::conds_upset(sol.pars, nsets = 28)
```



Deriving the conservative case and plotting it
with the QCAviz conditions function

```{r warning=FALSE}
sol.c <- reduced_c(temp_dta)
sol.cons <- solutions(sol.c)

#plotting the conditions
QCAviz::conds_upset(sol.cons, nsets = 15)
```


The configurations function for the simulated output
```{r}
config_upset_sim(sol.pars, nsets = 15)
config_upset_sim(sol.cons, nsets = 17)
```

















