---
title: "Working with the QCAviz package"
author: "Ingo Rohlfing, Ayjeren Rozyjumayeva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

QCA solutions that a researcher wants to aggregate can be created in different ways.

## Manual import of solutions
We use the original robustness analysis by Skaaning to illzstrate the manual import of solutions. (Skaaning, Svend-Erik (2011): Assessing the Robustness of Crisp-Set and Fuzzy-Set QCA Results. *Sociological Methods & Research* 40 (2): 391-408. [published version](http://10.1177/0049124111404818))

The following solutions are extracted from table 3 in the article that summarizes results for the choice of different calibration anchors for crisp-set QCA.
```{r Skaaning csqca anchors}
# crisp-set solutions with different anchors
one <- replicate(28, "DEV*STA")
two <- replicate(27, "DEV*ind+DEV*STA")
three <- replicate(165, "C")
four <- replicate(18, "DEV*LIT*STA")
five <- replicate(6, "DEV*STA+DEV*LIT*ind")
# combining solutions in list
Skaaning_csanchors <- list(one, two, three, four, five)
```

On the highest level of aggregation, one simply looks at the frequencies of the solutions.
```{r Skaaning csqca anchors sols}
sols_upset(Skaaning_csanchors, nsets = 5)
```

On the second, medium level of aggregation, the solutions are decomposed into their configurations. The `config_upset()` function serves this purpose.
```{r Skaaning csqca anchors configs}
config_upset(Skaaning_csanchors, nsets = 100)
```

```{r Skaaning csqca anchors conditions}
conds_upset(Skaaning_csanchors, nsets = 100)
```

Adding (to be edited later) application of the functions that allow for selection of the consistenc values.

```{r}
hinter <- read.csv("~hinterleitner2016.csv", sep = ";")

hinter <- hinter %>% 
  mutate(POScal = round(calibrate(pos, thresholds = "-2.4, -0.15, 1.4"), digits = 2)) %>% 
  mutate(AMBcal = round(calibrate(ambition, thresholds = "0.01, 0.1205, 0.2"), digits = 2)) %>% 
  mutate(CRcal = round(calibrate(CR, thresholds = c("5, 52, 95")), digits = 2)) %>% 
  mutate(DCcal = round(calibrate(DC, thresholds = c("33.5, 47, 55")), digits = 2)) %>% 
  mutate(EFFcal = round(calibrate(EFF, thresholds = c("0.7, 1.175, 2.065")), digits = 2)) %>%
  mutate(COMcal = round(calibrate(COM, thresholds = c("4.28, 4.86, 5.285")), digits = 2))

ttpos <- truthTable(data = hinter, outcome = "POScal", neg.out = FALSE,
                    conditions = c("AMBcal", "CRcal", "DCcal", 
                                   "EFFcal", "COMcal", "PRG"),
                    n.cut = 1, incl.cut1 = 0.837, sort.by = c("incl", "n"), 
                    complete = F, decreasing = T, show.cases = TRUE, PRI = F)

poscons <- minimize(ttpos, details = T, 
                 explain = "1", include = "1",
                 all.sol = T)

```


Applying the selector function itself and then the function within the UpSetR wrap function.

```{r}
dt.selector(poscons)
dt.selector(poscons, con.thresh = 0.85)
list.selector(solutionslist)
list.selector(solutionslist, con.thresh = 0.85)
```


Usage of the selectors within the QCAViz functions
```{r}
solutionslist <- list(poscons, poscons)

config_upset_1(poscons, y = 0.85, nsets = 10)
config_upset_h1(solutionslist, y = 0, nsets = 5)
```










